The Astropy Project

### 2017-11-10 main.tex
typo
more units

Central to the success of \astropy is an open environment where anybody can
contribute to the project by opening a so-called ``pull request'' with a new
contribution on a publically available
website\footnote{\url{https://github.com/astropy/astropy}}.
This request is then reviewed by at least one of the maintainers responsible for
the specific subpackage or content and is possibly merged into the main code
base.
Most bug fixes, documentation edits, and small features are contributed in this
way.
However, this model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces.
Thus, \astropy has a mechanism to more formally propose significant changes to
the core package (e.g., the release cycle; \citealt{ape2}), to plan out major
new features, or institute new organization-wide policies (e.g.,
\citealt{ape8}}).
This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
modeled after the ``Python Enhancement Proposals'' (PEP) and guide the
development of the \python programming language.
In an APE one or more authors describe in detail the proposed changes or
additions, including a rationale for the changes, how these changes will be
implemented, and, in the case of code, what the interface will be \citep{ape1}.
The APEs are discussed and refined by the community before much work is invested
into a detailed implementation; anyone is welcome to contribute to these
discussions during the open consideration period by leaving comments on the
respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}}
In previous APEs a community consensus emerged and APEs are accepted and become
the basis for future work at this point.
In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in question.

@@

In general we hope that becoming an affiliated package is seen as
a good way for new and existing packages to gain exposure.
%
\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages into the future section below}

@@

\section{Astropy Core Package v2.0}
\label{sec:core}

The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).

@@

The \texttt{astropy.units} subpackage adds support for representing units and
numbers with associated units (``quantities'') in code.
Historically, quantities in code have often been represented simply as numbers,
with units implied or noted via comments in the code because of considerations
about speed: having units associated with numbers inherently adds overhead to
numerical operations.
In \texttt{astropy.units}, \texttt{Quantity} objects subclass the \texttt{numpy}
array object and has been designed with speed in mind.
As of \astropypkg version 2.0, units and quantities are prevalent in most other
\astropypkg subpackages and are thus a key concept for using the package as a
whole.
The motivation and key concepts behind this subpackage were described in detail
in the previous paper \citep{astropy}, and thus here we primarily highlight new
features and improvements.

\begin{description}
    \item[Speed improvements] ...
    \item[Logarithmic units and magnitudes] ...
    \item[Using quantities in tables] In \astropypkg~2.0, one can also opt in to
        use quantities fully in tables, by using the {\tt QTable} class (see
        \sectionname~\ref{sec:table}). As a result, units in FITS tables are also
        well-supported. For most other modules, quantities are at least
        accepted, and often assumed by default.
    \item[Defining functions that require quantities] In the process, some
        standard wrappers have been defined that make defining functions that
        require quantities as input simpler. As an extension of this, we plan to
        define wrappers for functions that work on numbers that will
        automatically convert quantities to any required units.
    \item[Interaction with \package{numpy} arrays] ...
\end{description}

>>>>

Central to the success of \astropy is an open environment where anybody can
contribute to the project by opening a so-called ``pull request'' with a new
contribution on a publically available
website\footnote{\url{https://github.com/astropy/astropy}}.
This request is then reviewed by at least one of the maintainers responsible for
the specific subpackage or content and is possibly merged into the main code
base.
Most bug fixes, documentation edits, and small features are contributed in this
way.
However, this model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces.
Thus, \astropy has a mechanism to more formally propose significant changes to
the core package (e.g., the release cycle; \citealt{ape2}), to plan out major
new features, or institute new organization-wide policies (e.g.,
\citealt{ape8}).
This mechanism is called ``Astropy Proposal for Enhancement'' (APE) and are
modeled after the ``Python Enhancement Proposals'' (PEP) and guide the
development of the \python programming language.
In an APE one or more authors describe in detail the proposed changes or
additions, including a rationale for the changes, how these changes will be
implemented, and, in the case of code, what the interface will be \citep{ape1}.
The APEs are discussed and refined by the community before much work is invested
into a detailed implementation; anyone is welcome to contribute to these
discussions during the open consideration period by leaving comments on the
respective pull request.\footnote{\url{https://github.com/astropy/astropy-APEs}}
In previous APEs a community consensus emerged and APEs are accepted and become
the basis for future work at this point.
In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in question.

@@

\inlinecomment{APW}{This needs to be finished:}
In general we hope that becoming an affiliated package is seen as
a good way for new and existing packages to gain exposure.
%
\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages into the future section below}

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).

@@

The \texttt{astropy.units} subpackage adds support for representing units and
numbers with associated units (``quantities'') in code.
Historically, quantities in code have often been represented simply as numbers,
with units implied or noted via comments in the code because of considerations
about speed: having units associated with numbers inherently adds overhead to
numerical operations.
In \texttt{astropy.units}, \texttt{Quantity} objects subclass the \texttt{numpy}
array object and has been designed with speed in mind.
As of \astropypkg version 2.0, units and quantities are prevalent in most other
\astropypkg subpackages and are thus a key concept for using the package as a
whole.
Units are intimately entwined in the definition of astronomical coordinates and
thus nearly all functionality in the \texttt{astropy.coordinates} subpackage
(see \sectionname~\ref{sec:coordinates}) depends on this functionality.
For most other subpackages, quantities are at least accepted, and often expected
by default.

The motivation and key concepts behind this subpackage were described in detail
in the previous paper \citep{astropy}, and thus here we primarily highlight new
features and improvements.

\begin{description}
    \item[Speed improvements] \inlinecomment{TODO}{Marten}
    \item[Logarithmic units and magnitudes] \inlinecomment{TODO}{Marten}
    \item[Using quantities in tables] The \texttt{astropy.table} subpackage (see
        \sectionname~\ref{sec:table}) now supports using quantities in tables
        with the \texttt{QTable} class.
        As a result, units specified in FITS tables are supported, and tables
        with quantities can be read and written to various file formats.
    \item[Defining functions that require quantities] When writing code or
        functions that expect \texttt{Quantity} objects, we often want to
        enforce that the input units have the correct type.
        For example, we may want to require only length-type \texttt{Quantity}
        objects.
        These requirements often lead to implementing repetitive code for
        validating \texttt{Quantity} inputs.
        \texttt{astropy.units} now provides a \python decorator
        (\texttt{quantity_input}) that does this verification automatically.
    \item[Interaction with \package{numpy} arrays] \inlinecomment{TODO}{Marten}
\end{description}
